---
title: "Simple document"
author: Tanya Butt
date: September 16th, 2021
output: 
  html_document
  
---

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

#Section 3
Let's write a new code chunk.

This code chunk imports the stuff from last lecture.
These do different things to the code chunk below:
echo = FALSE
collapse = TRUE
eval = FALSE
message = FALSE removes tidyverse import warnings
```{r, message = FALSE}
library(tidyverse)

## set seed to ensure reproducibility
set.seed(1234)

## define data frame containing x and y
plot_df = tibble(
  x = rnorm(1000, sd = .5),
  y = 1 + 2 * x + rnorm(1000)
)

## histogram of x
ggplot(plot_df, aes(x = x)) + geom_histogram()

## scatterplot of x and y
ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

```{r, message = FALSE}
library(tidyverse)

## set seed to ensure reproducibility
set.seed(12)

## define data frame containing x and y
learning_df = tibble(
  sample = rnorm(500, mean = 1),
  sample_pos = sample > 0,
  abs_sample = abs(sample)
)

## histogram of x
ggplot(learning_df, aes(x = abs_sample)) + geom_histogram()

##median value of x
median_samp = median(pull(learning_df,sample))
```
The median of the variable containing absolute values is 
`r round(median_samp, digits = 2)`.
